%-------------------------
% Credits: https://github.com/sb2nov/resume for starter code
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontspec}
\usepackage{fontawesome}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-------------------------
\begin{center}
	\textbf{\huge Jaymin Suhagiya}  \\
	%\faGlobe \space \href{https://imdeep2905.github.io/}{imdeep2905.github.io } |  
	\faLinkedinSquare \space \href{https://www.linkedin.com/in/jaymin-suhagiya-809a25144/}{linkedin.com/in/jaymin-suhagiya} | \faGithub \space \href{https://github.com/jayminSuhagiya}{github.com/jayminSuhagiya} \\
	\faPhone \space \texttt{+}91-9664793283 |
	\faEnvelope \space \href{mailto:jaymin.suhagiya.ca@gmail.com}{jaymin.suhagiya.ca@gmail.com} \\
\end{center}
%-------------------------------------------

%-----------EDUCATION-----------------------
\section{Education}
\resumeSubHeadingListStart
    \resumeSubheading
    {Adani Institute of Infrastructure Engineering}{Ahmedabad, India}
	{B.E. in Information and Communication Technology;  CGPA: 9.6/10.0}{August 2017 - July 2021}
\resumeSubHeadingListEnd
%-------------------------------------------

%-----------EXPERIENCE----------------------
\section{Experience}
\resumeSubHeadingListStart
	
	%%% 1 %%%
	%\resumeSubheading
    %{FutureAPI}{Bengalore, India}
    %{Machine Learning Intern}{Oct 2020 - Present}
    %\resumeItemListStart
    %     \item TODO
    %\resumeItemListEnd
    
	%%% 2 %%%
	\resumeSubheading
    {Backend Developer }{Remote}
    {Memechat}{December 2021 - Present}
    \resumeItemListStart
         \item Rewrote and optimised (Query optimising and Reducing time complexity) every backend APIs from PHP to Python using FastAPI}.
         \item For {\bf Scalability and Cost optimisation} of the Memechat Application, worked on ProxySQL deployment.
	\item Monitoring metrics and deploying new updates in the Google cloud.
    \resumeItemListEnd
    
    	\resumeSubheading
    {Backend Developer }{Ahmedabad, India}
    {o2h Technology}{January 2021 - December 2021}
    \resumeItemListStart
         \item worked with frameworks like {\bf NodeJS, Laravel} and {\bf ReactJs} , as well as databases like  {\bf MongoDB, MySQL, DynamoDB} and {\bf Elasticsearch}.
         \item Worked in an Agile development cycle using advanced Scrum methodology and created user-friendly websites with different teams.
	\item In a weekly meetups, I shared my data structure and algorithm knowledge with the team, and I took the interviews and assessed the coding exam of freshers.
    \resumeItemListEnd


    
\resumeSubHeadingListEnd
%-------------------------------------------

%-----------PROJECTS------------------------
\section{Projects}
\resumeSubHeadingListStart
	%%% 1 %%%
%	\item {\bf Neural Network Sandbox \href{https://github.com/imdeep2905/Neural-Network-Sandbox}{\faGithub} | Python, Tensorflow, Pandas, Matplotlib, Kivy} 
%	\begin{itemize}
%		  \vspace*{-0.25cm}
%		\item This project provides {\bf GUI} for creating and training simple {\bf feed forward neural networks}.
%		\item Various {\bf hyper-parameters} can be tweaked from the GUI itself. It also supports {\bf visualization} of the {\bf network and training/testing statistics}.
%	\end{itemize}
	
	%%% 2 %%%

	\item {\bf Turing Q Learning (Multitasking Neural Network) \href{https://github.com/jayminSuhagiya/Turing-Q-Learning}{\faGithub}  | Python, Tensorflow, Reinforcement Learning} 
	\begin{itemize}
		  \vspace*{-0.25cm}
	\item Learned about reinforcement learning and different training meathods like Q Learning, DQN and DDQN.
		\item Build a multitasking neural network with the help of Reinforcement Learning. There is one bigger network common for multiple games and other small networks supporting the main network different for different network. 
	\item As a result, our newly developed neural network is capable of playing two different games.


	\end{itemize}

	\item {\bf Knapsack Container Loading Problem \href{https://github.com/imdeep2905/Coding-Challenge-Team-Vanished-Gradient}{\faGithub} \href{https://docs.google.com/viewer?url=https://github.com/imdeep2905/resume/blob/master/docs/CodingChallenge_certi.pdf?raw=true}{\faCertificate} | C\texttt{++}, Python, Matplotlib, tkinter} 
	\begin{itemize}
		  \vspace*{-0.25cm}
		\item We gave {\bf heuristic solution} for Knapsack Container Loading Problem which is {\bf NP-Hard} problem.
		\item Solution has support for both the {\bf GUI} and the {\bf solution visualisation}.
		\item It was developed in the {\bf team of 2} as a part of competition held at our college. We {\bf won the competition} by scoring {\bf 19/20}.
	\end{itemize}
	
	%%% 3 %%%

	%%% 4 %%%	
\resumeSubHeadingListEnd

%-------------------------------------------

%--------PROGRAMMING SKILLS-----------------
\section{Skills}
\resumeSubHeadingListStart
	\item {{\bf Proficient:} JavaScript, NodeJS, Laravel, MySQL, MongoDB, PHP, Python, C/C\texttt{++}, GIT protocol}
	\vspace*{-0.25cm}
	\item {{\bf Intermediate:} NextJS, ReactJS, ElasticSearch, Docker, FastAPI}
	\vspace*{-0.25cm}
	\item {{\bf Beginner:} Java,  CSS3, HTML5 }
\resumeSubHeadingListEnd
%-------------------------------------------

\section{Publications}
\resumeSubHeadingListStart
\item {\bf“Character Recognition on Time Series Data collected from Smartphone Sensors”}, Deep Raval et
al 2021 IOP Conf. Ser.: Mater. Sci. Eng. 1099 012014 .\href{https://iopscience.iop.org/article/10.1088/1757-899X/1099/1/012014}{\faExternalLink}
\item {\bf “Forecasting of Electricity Consumption for G20 Members Using Various Machine Learning
Techniques”}, Accepted book chapter to be published in: ‘Artificial Intelligence for Renewable Energy
Systems’, Scrivener Publishing partnered with John Wiley (USA)
\resumeSubHeadingListEnd
\section{Volunteer}
\resumeSubHeadingListStart
\item {\bf Unity of Youngistan(NGO)} \href{https://instagram.com/youngistan_official?utm_medium=copy_link}{\faExternalLink}
	\begin{itemize}
\item I participated in the {\bf Tree planting} event on World Environment Day organised by the NGO.
\item During the winter, I assisted in the distribution of blankets to those in need.
	\end{itemize}
\resumeSubHeadingListEnd

%--------ACHIEVEMENTS-----------------------
\section{Achievements}
\resumeSubHeadingListStart
\item I won the coding competition in a team of two held at our college based on an NP-Hard problem called the Knapsack container loading problem.
\item I played game called {\bf kho-kho} at state level in {\bf Khelmahakumbh} competition.
\item Completed {\bf Introduction to Tensorflow} Course on coursera provided by Deeplearning.ai
\item Learned {\bf Time Series and Sequence Model} on coursera.
\resumeSubHeadingListEnd
%-------------------------------------------
\end{document}